MPI3

### 2018-05-21 MiP3.Rmd
Adding data, sources, models

```{r setup, include=F}
knitr::opts_chunk$set(echo = TRUE) # Something about loading stuff more quickly 
library(tidyverse) # For data manipulation and visualization
library(stargazer) # For output tables 
library(plm) # For linear panel regression
library(car) # For logging the dependent variable; might be in tidyverse already 
library(gridExtra) # For multi-plot outputs 
library(maps) # Map data. May also be in tidyverse? 
library(mapdata) # More map data? 
library(R.utils) # capitalizing? 
library(MASS) # Boxcox? May also be in tidyverse? 
theme_set(theme_minimal()) # Sets default theme, I think  
```

```{r Data import, include=F}
#### Data ####
# Data from Michael Barber's work on political polarization: 
# https://doi.org/10.1086/683453
Barber <- read_csv("~/Documents/GitHub/Money-in-Politics/data/Barber/Barber_Limits_Data.csv")
# Getting 2008 only data (reasons for which will become clear in the next sections)
# They didn't get clearer. 
# Barber2008 <- Barber %>% filter(year==2008)

@@

#### Plotting Barber #### 
ind_limits_2010.plot <- ggplot(Barber, aes(ind_limits_2010)) + geom_density() + theme_minimal()
ind2pty_limits_2010.plot <- ggplot(Barber, aes(ind2pty_limits_2010)) + geom_density() + theme_minimal()
pac_limits_2010.plot <- ggplot(Barber, aes(pac_limits_2010)) + geom_density() + theme_minimal()
Barber.plots <- grid.arrange(ind_limits_2010.plot, ind2pty_limits_2010.plot, pac_limits_2010.plot, nrow=1)
# ![](Barber.plots.png)
```

@@

```{r ICS density plots, include=F=F}
grid.arrange(CCIdensity, CRIdensity, nrow=1)
```

@@

>>>>

```{r setup, include=F, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE) # Something about loading stuff more quickly 
library(tidyverse) # For data manipulation and visualization
library(stargazer) # For output tables 
library(plm) # For linear panel regression
library(car) # For logging the dependent variable; might be in tidyverse already 
library(gridExtra) # For multi-plot outputs 
library(maps) # Map data. May also be in tidyverse? 
library(mapdata) # More map data? 
library(R.utils) # capitalizing? 
library(MASS) # Boxcox? May also be in tidyverse? 
theme_set(theme_minimal()) # Sets default theme, I think  
```

```{r Data import, include=FALSE}
#### Data ####
# Data from Michael Barber's work on political polarization: 
# https://doi.org/10.1086/683453
Barber <- read_csv("~/Documents/GitHub/Money-in-Politics/data/Barber/Barber_Limits_Data.csv")
# Getting 2008 only data (reasons for which will become clear in the next sections)
# They didn't get clearer. 
# Barber2008 <- Barber %>% filter(year==2008)

@@

#### Plotting Barber #### 
ind_limits_2010.plot <- ggplot(Barber, aes(ind_limits_2010)) + geom_density() + theme_minimal()
ind_limits_2010.plot
ind2pty_limits_2010.plot <- ggplot(Barber, aes(ind2pty_limits_2010)) + geom_density() + theme_minimal()
ind_limits_2010.plot
pac_limits_2010.plot <- ggplot(Barber, aes(pac_limits_2010)) + geom_density() + theme_minimal()
Barber.plots <- grid.arrange(ind_limits_2010.plot, ind2pty_limits_2010.plot, pac_limits_2010.plot, nrow=1)
pac_limits_2010.plot
# ![](Barber.plots.png)
```

@@

```{r ICS density plots, include=F}
grid.arrange(CCIdensity, CRIdensity, nrow=1)
```

@@

```{r replication data maybe}
library(haven)
Campante <- read_dta("data/Replication/CampanteDo_MainData.dta")
```
